---
title: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include = FALSE}
pkgCheck <- function(packages){
    for(x in packages){
        try(if (!require(x, character.only = TRUE)){
            install.packages(x, dependencies = TRUE)
            if(!require(x, character.only = TRUE)) {
                stop()
            }
        })
    }
}
pkgCheck(c("flexdashboard", "ggplot2", "gridExtra"))
files <- list.files(pattern = "^(salleElevage_)(.)*(csv)$")
numSensors <- 8
bdd <- lapply(files, function(myFile){
	read.table(myFile, header = TRUE, sep = ";", dec = ".")
})
bdd <- do.call(rbind, bdd)
bdd$dateTime <- as.POSIXlt(
  paste0(bdd$year, "-", 
         bdd$month, "-", 
         bdd$day, " ", 
         bdd$hour, ":", 
         bdd$minute, ":", 
         bdd$second))
bdd$temperature[bdd$temperature == 85.0] <- NA 
bdd$sensorId <- as.character(bdd$sensorId)
bdd$sensorId[bdd$sensorId == "28-00000ac82be5"] <- "SNK_Mak_bib_26"
bdd$sensorId[bdd$sensorId == "28-00000ac82d99"] <- "SNK_Mak_cage_21"
bdd$sensorId[bdd$sensorId == "28-00000ac8bafe"] <- "SNF_bib_26"
bdd$sensorId[bdd$sensorId == "28-00000ac8a098"] <- "SNF_cage_21"
bdd$sensorId[bdd$sensorId == "28-00000ac89b2d"] <- "Ext1"
bdd$sensorId[bdd$sensorId == "28-00000ac8aa0f"] <- "Ext2"
bdd$sensorId[bdd$sensorId == "28-00000ac85b0c"] <- "SNK_Kob_bib_26"
bdd$sensorId[bdd$sensorId == "28-00000ac84a81"] <- "SNK_Kob_cage_21"
tempRange <- list(
  c(24, 28), c(19, 23), c(24, 28), c(19, 23), 
  c(15, 30), c(15, 30), c(24, 28), c(19, 23)
)
sensNames <- c("SNK_Mak_bib_26", "SNK_Mak_cage_21", 
               "SNF_bib_26", "SNF_cage_21", "Ext1", 
               "Ext2", "SNK_Kob_bib_26", "SNK_Kob_cage_21")
```

overview
===================================== 

### overview

```{r, fig.width = 20, fig.height = 14}
bddY <- tail(bdd, numSensors*60*7*4*24)
par(mfrow = c(2, 4))
gg01 <- lapply(seq_along(sensNames), function(i){
  bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
  aggHour <- aggregate(bddY_sens$temperature ~ 
    format(as.POSIXct(bddY_sens$dateTime),
    "%y-%m-%d"), data = bddY_sens, mean, na.rm = TRUE)
  names(aggHour) <- c("dateTime", "temperature")
  aggHourMin <- aggregate(bddY_sens$temperature ~ 
    format(as.POSIXct(bddY_sens$dateTime),
    "%y-%m-%d"), data = bddY_sens, min, na.rm = TRUE)
  names(aggHourMin) <- c("dateTime", "temperature")
  aggHourMax <- aggregate(bddY_sens$temperature ~ 
    format(as.POSIXct(bddY_sens$dateTime),
    "%y-%m-%d"), data = bddY_sens, max, na.rm = TRUE)
  names(aggHourMax) <- c("dateTime", "temperature")
  
  p <- ggplot() 
  p <- p + geom_line(data = aggHour, aes(
    x = dateTime, y = temperature, 
    group = 1), size = 1)
  p <- p + geom_line(data = aggHourMin, aes(
    x = dateTime, y = temperature, 
    group = 1), size = 1, col = 4)
  p <- p + geom_line(data = aggHourMax, aes(
    x = dateTime, y = temperature, 
    group = 1), size = 1, col = 2)
  p <- p + scale_y_continuous(limits = tempRange[[i]]) + 
    labs(x = "", y = "Temperature", 
      title = sensNames[i])
  p <- p + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
  return(p)
})
grid.arrange(gg01[[1]], gg01[[2]], gg01[[3]], gg01[[4]], 
             gg01[[5]], gg01[[6]], gg01[[7]], gg01[[8]], ncol = 4)
```


SNK_Mak_bib_26
=====================================

```{r}
i <- 1
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```


SNK_Mak_cage_21
=====================================

```{r}
i <- 2
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

SNF_bib_26
=====================================

```{r}
i <- 3
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

SNF_cage_21
=====================================

```{r}
i <- 4
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

Ext1
=====================================

```{r}
i <- 5
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

Ext2
=====================================

```{r}
i <- 6
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

SNK_Kob_bib_26
=====================================

```{r}
i <- 7
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

SNK_Kob_cage_21
=====================================

```{r}
i <- 8
bddY_sens <- bddY[bddY$sensorId == sensNames[i],]
aggHour <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, mean, na.rm = TRUE)
names(aggHour) <- c("dateTime", "temperature")
aggHourMin <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, min, na.rm = TRUE)
names(aggHourMin) <- c("dateTime", "temperature")
aggHourMax <- aggregate(bddY_sens$temperature ~ 
  format(as.POSIXct(bddY_sens$dateTime),
  "%Y-%m-%d %H"), data = bddY_sens, max, na.rm = TRUE)
names(aggHourMax) <- c("dateTime", "temperature")
sumStats <- summary(bddY_sens$temperature)
```

Row
-------------------------------------

### Min.
```{r}
valueBox(round(sumStats[1], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[1] < tempRange[[i]][1], "warning", "primary"))
```

### 1st Qu.
```{r}
valueBox(round(sumStats[2], digits = 2), 
         icon = "fa-thermometer-quarter", 
         color = ifelse(sumStats[2] < tempRange[[i]][1], "warning", "primary"))
```

### Median
```{r}
valueBox(round(sumStats[3], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[3] < tempRange[[i]][1] | sumStats[3] > tempRange[[i]][2], 
           "warning", "primary"))
```

### Mean
```{r}
valueBox(round(sumStats[4], digits = 2), 
         icon = "fa-thermometer-half", 
         color = ifelse(
           sumStats[4] < tempRange[[i]][1] | sumStats[4] > tempRange[[i]][2], 
           "warning", "primary"))
```

### 3rd Qu.
```{r}
valueBox(round(sumStats[5], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[5] > tempRange[[i]][2], "warning", "primary"))
```

### Max.
```{r}
valueBox(round(sumStats[6], digits = 2), 
         icon = "fa-thermometer-three-quarters", 
         color = ifelse(sumStats[6] > tempRange[[i]][2], "warning", "primary"))
```

Row
-------------------------------------

### boxplot with breaks every hour

```{r}
p <- ggplot(data = bddY_sens, aes(x = format(as.POSIXct(bddY_sens$dateTime), 
  "%y-%m-%d"), y = temperature))
p <- p + geom_boxplot(outlier.colour="red")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(limits = c(
	min(bddY_sens$temperature, na.rm = TRUE), 
	max(bddY_sens$temperature, na.rm = TRUE))) + 
  labs(x = "", y = "Temperature", 
    title = sensNames[i])
p
```

